\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-26 paper/manuscript.tex
made most of the requested changes with respect to the stm

The results are shown in table \ref{stmResultsTable}. The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom [@markus, would you please add a sentence indicating how we measured how R/D a topic was (e.g., the magnitude of the coefficient)?]. The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.  [@markus, do the results from the stm package allow us to say anything about whether the overall fit of the model improved from adding party? if so, can we mention that?].

Many of the topics associated with Democrats fit with what we understand to be national party priorities [@markus, please reference topic numbers in the next two sentences]. Topic [@markus] is related to education. Topic [@markus]  is related to recycling. Topic 44, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Similarly, employee rights are represented in Topic 46. Democrats also exhibit a strong preference for words related to public finances, such as Topic 22 ('budget', 'revenue', 'expenditure') as well as Topic 17 ('debt', 'bond', 'financial'). We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money. This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement---a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}). [@markus, would you please elaborate on why this is "complicated"]. Finally, Democrats also focus more on the deliberative process of policymaking, as topics 29 ('election', 'agenda', 'committee'), 39 ( `comment', `draft', `review'), 50 (`aye', `absent', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.

>>>>

The results are shown in table \ref{stmResultsTable}. The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom. The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic. The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.  [@markus, do the results from the stm package allow us to say anything about whether the overall fit of the model improved from adding party? if so, can we mention that?].

Many of the topics associated with Democrats fit with what we understand to be national party priorities. Topic 44, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Similarly, employee rights are represented in Topic 46. Democrats also exhibit a strong preference for words related to public finances, such as Topic 22 ('budget', 'revenue', 'expenditure') as well as Topic 17 ('debt', 'bond', 'financial'). We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money. This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement. On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}. On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}. Finally, Democrats also focus more on the deliberative process of policymaking, as topics 29 ('election', 'agenda', 'committee'), 39 ( `comment', `draft', `review'), 50 (`aye', `absent', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
